### 2023-11-11 thesis/sections/1-introduction.tex
bibliography

\section{Introduction}
\label{sec:introduction}
Language is a complex system that enables humans to communicate and convey meaning. However, the mere existence of words and grammatical structures is not enough to guarantee effective communication. Without grounding, language remains detached from the physical world, making it difficult for individuals to comprehend and interpret linguistic expressions accurately.
Grounding bridges the gap between abstract linguistic representations and concrete experiences, providing a shared context and reference point for language users \citep{Roy2002,Bisk2020,Bender2020}. By linking language to sensory perceptions, physical experiences, and the situational context, grounding enhances comprehension, facilitates communication.
However, one challenge lies in how arbitrary symbols in language can be connected to real-world objects and concepts and acquire meaning, described as the symbol grounding problem by \citet{Harnad1999}.
Artificial agents can be taught grounding in different ways.
One approach is to show the agent an image of the scene as visual input together with a textual description of what is to be grounded in this scene.
This can be for example a description of the whole scene, certain visible objects or also actions that are happening \citep{Ahrens2022,Ilinykh2022,Lu2016,Mitchell2013}.
By doing this, the agents can learn to identify the same descriptions and symbols for similar visual input.
In other approaches, the agents can learn to ground language in visual input through interaction and dialogue, either with humans or other agents.
Thus, agents might develop certain strategies to ground language efficiently \citep{Dobnik2018,Dobnik2021,Zarriess2019}.

@@

Meaning of symbols and referring expression emerge through dialogue between interlocutors \citep{Wittgenstein1953,Clark1986}.
Moreover, \citet{Wittgenstein1953} introduces the concept of \emph{language games}: small parts of conversation between interlocutors.
In these language games, the emerged meaning of the referring expressions depends on their context.
This reasoning was taken up in training artificial agents to learn to refer to entities.
Hereby, agents need to communicate arbitrary symbols to each other in multiple turns to solve a given task.
By solving the task, they assign meaning to these symbols and an artificial language emerges.
This setup allows to control the architecture of the agents, the information the agents receive, how and what they are able to communicate and which goals they are trained on.
By this, their behavior and the emergence of referring expressions can be studied precisely and consistently.
In early research, agents and their communication were studied in the context of robotics and rule-based systems \citep{Steels2009,Roy2002,Kirby2002,Kirby2008}, while in current research, agents are based on deep neural networks \citep{Lazaridou2017,Baroni2020,Baroni2022,Kottur2017}
Furthermore, a focus lies on the nature of the emerged language.
Agents can for instance learn a compositional language that allows them to combine already learned symbols to create new meaning, when presented with a changed environment and unseen situations \citep{Kharitonov2020,Lazaridou2018,Gupta2020}.
Additionally, emergent languages can be learned to encode meaning in efficient ways \citep{Chaabouni2019,Zaslavsky2018}.

>>>>

\section{Introduction}
\label{sec:introduction}
Language is a complex system that enables humans to communicate and convey meaning. However, the mere existence of words and grammatical structures is not enough to guarantee effective communication. Without grounding, language remains detached from the physical world, making it difficult for individuals to comprehend and interpret linguistic expressions accurately.
Grounding bridges the gap between abstract linguistic representations and concrete experiences, providing a shared context and reference point for language users \citep{Roy2002,Bisk2020,Bender2020}. By linking language to sensory perceptions, physical experiences, and the situational context, grounding enhances comprehension, facilitates communication.
However, one challenge lies in how arbitrary symbols in language can be connected to real-world objects and concepts and acquire meaning, described as the symbol grounding problem by \citet{Harnad1999}.
Artificial agents can be taught grounding in different ways.
One approach is to show the agent an image of the scene as visual input together with a textual description of what is to be grounded in this scene.
This can be for example a description of the whole scene, certain visible objects or also actions that are happening \citep{Ahrens2022,Ilinykh2022,Lu2017,Mitchell2013}.
By doing this, the agents can learn to identify the same descriptions and symbols for similar visual input.
In other approaches, the agents can learn to ground language in visual input through interaction and dialogue, either with humans or other agents.
Thus, agents might develop certain strategies to ground language efficiently \citep{Dobnik2018a,Dobnik2021,Zarriess2019}.

@@

Meaning of symbols and referring expression emerge through dialogue between interlocutors \citep{Wittgenstein1953,Clark1986}.
Moreover, \citet{Wittgenstein1953} introduces the concept of \emph{language games}: small parts of conversation between interlocutors.
In these language games, their context defines which meaning emerges for the referring expressions.
This reasoning was taken up in training artificial agents to learn to refer to entities.
Hereby, agents need to communicate arbitrary symbols to each other in multiple turns to solve a given task.
By solving the task, they assign meaning to these symbols and an artificial language emerges.
This setup allows to control the architecture of the agents, the information the agents receive, how and what they are able to communicate and which goals they are trained on.
By this, their behavior and the emergence of referring expressions can be studied precisely and consistently.
In early research, agents and their communication were studied in the context of robotics and rule-based systems \citep{Steels2009,Roy2002,Kirby2002,Kirby2008}, while in current research, agents are based on deep neural networks \citep{Lazaridou2017,Baroni2020,Baroni2022,Kottur2017}
Furthermore, a focus lies on the nature of the emerged language.
Agents can for instance learn a compositional language that allows them to combine already learned symbols to create new meaning, when presented with a changed environment and unseen situations \citep{Kharitonov2020,Lazaridou2018,Gupta2020}.
Additionally, emergent languages can be learned to encode meaning in efficient ways \citep{Chaabouni2019,Zaslavsky2018}.

### 2023-11-11 thesis/sections/2-background.tex
describe experimental setups
bibliography

\subsection{Grounding}
\cmtDK[inline]{importance of grounding and what it is}

\subsection{Referring expressions}
\cmtDK[inline]{what are referring expressions and how are they studied (generation, understanding, ...)}
\cmtDK[inline]{incremental GRE algorithm from Dale}
Even though, recent large language models (LLMs) such as BERT \citep{Devlin2019} or GPT-3 \citep{Brown2020} produce impressive results on many tasks in Natural Language Processing, they are often only trained on big amounts of text corpora.
In this way, their only way of learning, how to generate language as well as solve these tasks is to find patterns of how words and sentences are used in these large corpora.
Many researchers criticize this approach, by arguing that these model can't learn meaning just by learning on text.
In \citep{Bender2020}, the authors argue that meaning is bound to a communicative intent.
These are the purposes of why humans are using language.
The intent is always embedded in a broader context that exists outside the language itself.
This context includes the real world, but also the background knowledge of the speaker as well as interlocutors or reason for what the speaker is saying.
By grounding the intent in this context, it becomes meaningful.
Only with this step, the intent can be interpreted by the listeners.
% This intent is connected to the real world that exists outside of language, in other words it is grounded in the world.
% SD: Not just real world, also to background knowledge and what the person wants to do. 
% SD: Grounding is more related to interpretability of expressions rather than intent. Without grounding they cannot be interpreted. The intent shapes WHAT referring expressions are generated in what contexts of the real world.   Hence, intent is a meta thing connecting world, language, knowledge and agent’s experience.
% DK: first part included, referring expressions are included below (done)
This grounding is missing, when models only train on abstract textual representations of the world.
\citet{Bisk2020} argues that a multimodal approach, including for instance perception as well as social context, is needed to learn meaning in a broader context.
One added modality to ground language is often vision. \cmtDK{cite}
Hereby, the model needs to learn how to associate linguistic concepts in text corpora with features, extracted from visual input.
For instance, a model can learn to associate the noun "dog" with an animal seen in an image or associate the action of "jumping over" with the animal being above an object.

>>>>

\subsection{Grounding}
\cmtDK[inline]{importance of grounding and what it is}
Even though, recent large language models (LLMs) such as BERT \citep{Devlin2019} or GPT-3 \citep{Brown2020} produce impressive results on many tasks in Natural Language Processing, they are often only trained on big amounts of text corpora.
In this way, their only way of learning, how to generate language as well as solve these tasks is to find patterns of how words and sentences are used in these large corpora.
Many researchers criticize this approach, by arguing that these model can't learn meaning just by learning on text.
In \citep{Bender2020}, the authors argue that meaning is bound to a communicative intent.
These are the purposes of why humans are using language.
The intent is always embedded in a broader context that exists outside the language itself.
This context includes the real world, but also the background knowledge of the speaker as well as interlocutors or reason for what the speaker is saying.
By grounding the intent in this context, it becomes meaningful.
Only with this step, the intent can be interpreted by the listeners.
% This intent is connected to the real world that exists outside of language, in other words it is grounded in the world.
% SD: Not just real world, also to background knowledge and what the person wants to do. 
% SD: Grounding is more related to interpretability of expressions rather than intent. Without grounding they cannot be interpreted. The intent shapes WHAT referring expressions are generated in what contexts of the real world.   Hence, intent is a meta thing connecting world, language, knowledge and agent’s experience.
% DK: first part included, referring expressions are included below (done)
This grounding is missing, when models only train on abstract textual representations of the world.
\citet{Bisk2020} argues that a multimodal approach, including for instance perception as well as social context, is needed to learn meaning in a broader context.
One added modality to ground language is often vision.
Hereby, the model needs to learn how to associate linguistic concepts in text corpora with features, extracted from visual input.
For instance, a model can learn to associate the noun "dog" with an animal seen in an image or associate the action of "jumping over" with the animal being above an object.

\subsection{Referring expressions}
\cmtDK[inline]{what are referring expressions and how are they studied (generation, understanding, ...)}
\cmtDK[inline]{incremental GRE algorithm from Dale}
